\Large{Adversarial Variational Optimization of Non-Differentiable Simulators}

### 2017-07-15 tex/paper.tex
save

Lastly, we make a connection to Operator Variational Inference (OPVI)~\citep{2016arXiv161009033R},
which is a generalization of variational inference formulated as the following optimization problem:
\begin{eqnarray}
\bflambda^* = \inf_\bflambda \sup_\bfphi \mathbb{E}_{ \bfz \sim q( \bfz | \bflambda)} [ (O^{p,q} f_\bfphi) ] \, .
\end{eqnarray}
In traditional VI with the KL distance, we have $(O^{p,q} f) = \log q(\bfz) - \log p(\bfz|\bfx) \, \forall f \in \mathcal{F}$.
AVO can be cast into a similar form with expectations over $\bfx$ instead of $\bfz$ and
\begin{eqnarray} \label{eq:opvi_avo}
\bfpsi^* &=& \inf_\bfpsi \sup_\bfphi \mathbb{E}_{ \bfx \sim q( \bfx | \bfpsi)} [ (O^{p_r,q_\bfpsi} d_\bfphi) ] \\
\label{eq:opvi_avo2} &=&  \inf_\bfpsi \sup_\bfphi \mathbb{E}_{\bfx\sim p_r(\bfx)}[d(\bfx; \bfphi)] - \mathbb{E}_{\bfx \sim q(\bfx|\bfpsi)}[d(\bfx; \bfphi)] \nonumber \, .
\end{eqnarray}
Rewriting Eqn.~\ref{eq:opvi_avo} as above is possible through importance sampling,
corresponding to an implicit form of the operator
\begin{equation}
(O^{p_r,q_\bfpsi} d_\bfphi)(\bfx) = \left( \frac{p_r(\bfx)}{q(\bfx|\bfpsi)}  -1 \right) d(\bfx; \bfphi) \, ,
\end{equation}
which reinforces the link to density ratio estimation and inference with implicit models.

@@

\vspace{0.25cm}
\subsection*{Acknowledgments}

@@

>>>>

Lastly, we make a connection to Operator Variational Inference (OPVI)~\citep{2016arXiv161009033R},
which is a generalization of variational inference formulated as the following optimization problem:
\begin{eqnarray}
\bflambda^* = \inf_\bflambda \sup_\bfphi \mathbb{E}_{ \bfz \sim q( \bfz | \bflambda)} [ (O^{p,q} f_\bfphi) ] \, .
\end{eqnarray}
In traditional VI with the KL distance, this corresponds to $(O^{p,q} f)(\bfz) = \log q(\bfz) - \log p(\bfz|\bfx) \, \forall f \in \mathcal{F}$.
AVO can be cast into a similar form with expectations over $\bfx$ instead of $\bfz$ and
\begin{eqnarray} \label{eq:opvi_avo}
\bfpsi^* &=& \inf_\bfpsi \sup_\bfphi \mathbb{E}_{ \bfx \sim q( \bfx | \bfpsi)} [ (O^{p_r,q_\bfpsi} d_\bfphi) ] \\
\label{eq:opvi_avo2} &=&  \inf_\bfpsi \sup_\bfphi \mathbb{E}_{\bfx\sim p_r(\bfx)}[d(\bfx; \bfphi)] - \mathbb{E}_{\bfx \sim q(\bfx|\bfpsi)}[d(\bfx; \bfphi)] \nonumber \, .
\end{eqnarray}
Rewriting Eqn.~\ref{eq:opvi_avo} as above is possible through importance sampling,
corresponding to an implicit form of the operator
\begin{equation}
(O^{p_r,q_\bfpsi} d_\bfphi)(\bfx) = \left( \frac{p_r(\bfx)}{q(\bfx|\bfpsi)}  -1 \right) d(\bfx; \bfphi) \, ,
\end{equation}
which reinforces the link to density ratio estimation and inference with implicit models.

@@

\vspace{0.4cm}
\section*{Acknowledgments}

@@

\vspace{2cm}
